Regular singular Volterra equations on complex domains

### 2023-07-27 reg-sing-volterra.tex
Fill in more details about regular singular Volterra equations
Describe setting, fill in reasoning about prototype solution, and show
inclusions between weighted holomorphic L-infinity spaces.

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{eqnarray}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor} %% for revisions
\usepackage{xparse} %% for squiggly underlines
\usepackage{tikz-cd} %% for term norm scratch work

@@

@@

% operator under consideration
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_\text{hard}}
\newcommand{\softpart}{\mathcal{V}_\text{soft}}

@@

If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
\subsection{Main result}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect. It's an improved version of the result stated in Section~\ref{frac_int_exist}, which is copied from {\tt airy-resurgence}. Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}
\begin{thm}
Let $\Omega$ be an acute-angled open sector around $\zeta = 0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.} Over $\Omega$, consider a Volterra operator
\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R}, \]
where
\begin{itemize}
\item $p$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item a simple zero at $\zeta = 0$,
\item no zeros in $\Omega$ (as the next condition implies), and
\item a positive lower bound $C_p |z|^d \le |p|$;
\end{itemize}
\item $q$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item an upper bound $|q| \le C_q |z|^{d-1}$; and
\end{itemize}
\item $\mathcal{R}$ is an integral kernel operator
\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta, \]
where $k$ is a holomorphic function on $\Omega^2$, with
\begin{itemize}
\item an exponential upper bound $k(a, a') \le C_k e^{A|\zeta(a) - \zeta(a')|}$.
\end{itemize}
\end{itemize}
Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$, and let $\tau = q_0 / p_1$.

For any $\epsilon > 0$, when the constant $\Lambda > A$ is large enough, the regular singular Volterra equation
\[ \mathcal{V}f = 0 \]
has a unique solution in the affine subspace
\[ \zeta^{\tau-1} + \holoL{\infty, \tau-1+\epsilon}_\Lambda(\Omega) \]
of the function space $\holoL{\infty, \tau-1}_\Lambda(\Omega)$, defined in Section~\ref{fn-spaces}.
\end{thm}
%%\begin{thm}
%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}

@@

%%Under these conditions, let's try to solve the regular singular Volterra equation
%%\[ \mathcal{V}f = 0. \]
%%The leading-order part of the equation,
%%\[ \big[p_1 \zeta + \partial^{-1} \circ q_0\big]f = 0, \]
%%has $\zeta^{\tau-1}$ as a solution, where $\tau = p_1/q_0$. If we guess that the function spaces defined in Section~\ref{fn-spaces} are well suited for this problem, we might hope for the full equation to have a solution of the form
%%\[ f = \zeta^{\tau-1} + f_*, \]
%%where $f_* \in \holoL{\infty, 1-\tau-\epsilon}_Z(\Omega)$ for some $Z \in \C$. When $Z\Omega$ is in the right half-plane and $|Z|$ is large enough, there is in fact a unique solution of this form.
%%\end{thm}
\section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
\subsection{Weighted holomorphic $L^\infty$ spaces}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\cont(\Omega)$ be the space of continuous complex-valued functions on $\Omega$. Give $\cont(\Omega)$ the compact-open topology, recalling that this is the finest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \Omega$~\cite[Example~2.6 and \S 4 notes]{fnl-cpx-anal}. The holomorphic functions form a closed subspace $\holo(\Omega) \subset \cont(\Omega)$~\cite[Proposition~3.14]{fnl-cpx-anal}\textcolor{orange}{[Luecking \& Rubel]}.

Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\Omega$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$. One might describe these functions as being uniformly of exponential type $\Lambda$. They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$. With respect to the seminorm on $\holo(\Omega)$ given by a compact set $K \subset \Omega$, the inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
\begin{prop}\label{exp-complete}
The space $\singexp{0}{\Lambda}(\Omega)$ is complete.
\end{prop}
\begin{proof}
\textcolor{orange}{[Check!]} Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$. The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$, as discussed above, so our sequence is Cauchy in $\holo(\Omega)$ too. Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal}, our sequence converges to a function $f$ there.

The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ tells us that for any $r > 0$, we can find some $n$ for which $e^{-\Lambda |\zeta|} |f_k - f_n| \le r$ whenever $k \ge n$. Since convergence in $\holo(\Omega)$ implies pointwise convergence, we can see as $k$ grows that $e^{-\Lambda |\zeta|} |f - f_n| \le r$. This shows that our sequence converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$. We can also use the Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ to bound the norms $\|f_n\|_{0,\Lambda}$. Then, from the pointwise convergence argument above, we can draw the additional conclusion that $f$ is in $\singexp{0}{\Lambda}(\Omega)$.
\end{proof}

Now, let's relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$. Let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$. Give it the norm $\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|$. Reprising the arguments from above, we can show that the inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is continuous, and we can generalize Proposition~\ref{exp-complete}:
\begin{prop}
The space $\singexp{\sigma}{\Lambda}(\Omega)$ is complete.
\end{prop}
%%Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. For any $\sigma \in \R$ and $Z \in \C$, multiplying by $\zeta^\sigma e^{\Re(Z\zeta)}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$. We'll call this space $\expHoloL{\infty, \sigma}{Z}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma; Z} = \|\zeta^{-\sigma} e^{-\Re(Z\zeta)} f\|_\infty$, so that
%%\begin{align*}
%%\holoL{\infty}(\Omega) & \to \expHoloL{\infty, \sigma}{Z}(\Omega) \\
%%\varphi & \mapsto \zeta^\sigma e^{\Re(Z\zeta)} \varphi
%%\end{align*}
%%is an isometry. More generally,
%%\begin{align*}
%%\expHoloL{\infty, \rho}{Z}(\Omega) & \to \expHoloL{\infty, \rho+\delta}{Z}(\Omega) \\
%%f & \mapsto \zeta^\delta f
%%\end{align*}
%%is an isometry for all $\rho, \delta \in \R$ and $Z \in \C$. This reduces to the previous statement when $\rho = 0$ and $Z = 0$.
%%\subsection{Graded algebra structure}
%%For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho-\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho-\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$.
%%\begin{verify}
%%\begin{align*}
%%\|f\|_{\infty, \rho+\delta, Z} & = \|\zeta^{-(\rho-\delta)} e^{-\Re(Z\zeta)} f\|_\infty \\
%%& = \|\zeta^\delta \zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty \\
%%& = \|\zeta^\delta\|_\infty\,\|\zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty & \text{(Banach algebra)} \\
%%& \le \|\zeta^\delta\|_\infty\,\|f\|_{\infty, \rho; Z}
%%\end{align*}
%%\end{verify}
%%Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\expHoloL{\infty, -\infty}{Z}(\Omega) := \bigcup_{\sigma \in \R} \expHoloL{\infty, \sigma}{Z}(\Omega)$ is a graded algebra, with a different norm on each grade. For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.
%%\subsection{Norms of effectively finite-order operators}
%%\begin{itemize}
%%\item Say $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$. For any $f \in \expHoloL{\infty, \rho}{Z}$,
%%\begin{align*}
%%\|mf\|_{\infty, \sigma; Z} =
%%\end{align*}
%%\end{itemize}

>>>>

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{eqnarray}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor} %% for revisions
\usepackage{xparse} %% for squiggly underlines
\usepackage{tikz-cd} %% for term norm scratch work
\usepackage{tikz}

% TikZ libraries
\usetikzlibrary{bbox}
\usetikzlibrary{fadings}

% hat tip TeX.SE user marsupilam - https://tex.stackexchange.com/a/351570/6934
%%\tikzfading[
%%  name=radial,
%%  inner color=transparent!0,
%%  outer color=transparent!100
%%]
% hat tip TeX.SE user Andrew Stacey
%   https://tex.stackexchange.com/a/82503/6934
%   https://tex.stackexchange.com/questions/82425/tikz-radial-shading-of-a-ring#comment176908_82503
\pgfdeclareradialshading{infinifade}{\pgfpointorigin}{%
  color(0bp)=(transparent!0);
  color(20bp)=(transparent!0);
  color(22bp)=(transparent!10);
  color(24bp)=(transparent!90);
  color(25bp)=(transparent!100)
}
\pgfdeclarefading{infinity}{\pgfuseshading{infinifade}}%

@@

% format lists
\setlist[itemize]{leftmargin=15mm}
\makeatletter
% hat tip TeX.SE user31729
%   https://tex.stackexchange.com/a/328393/6934
\newcommand{\cond}[1]{\item[(\textsc{#1})]\protected@edef\@currentlabel{\textsc{#1}}}
\makeatother

@@

% operator under consideration
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_\text{basic}}
\newcommand{\softpart}{\mathcal{V}_\text{extra}}
\newcommand{\hardker}{k_\text{basic}}
\newcommand{\softker}{k_\text{extra}}

@@

If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
\subsection{Setting}
\subsubsection{The domain}\label{setting:domain}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$. For some of our results, we'll need an extra condition on $\domain$:
\begin{itemize}
\cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$. In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$. Since $\domain$ doesn't contain $\zeta = 0$, we'll always leave that starting point out of the path.
\end{itemize}
For the applications we have in mind, $\domain$ might look something like the set pictured below, which satisfies Condition~\eqref{cond:star}.
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=infinity]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
\end{tikzpicture}
\end{center}
\subsubsection{The prototype operator}\label{setting:basic}
The prototypical example of the kind of operator we'll be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.

Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
\[ \hardker(a, a') = \frac{q(a')}{p(a)}, \]
where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means that for some constant $\tau$---the {\em residue} of the singularity---the difference
\[ -\frac{\tau}{\zeta(a)} - \hardker(a, a') \]
is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\Omega^2$. We'll assume that $\tau$ is real and positive.

Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
\begin{verify}
[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded. By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition. Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
\end{verify}
For some of our results, we'll also need to keep $|p|$ and $|q|$ under control as $|\zeta|$ goes to infinity.
\begin{itemize}
\cond{slow}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
\begin{align*}
\left|\frac{1}{p}\right| & \le e^{\lambda_p |\zeta|} &
\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
\end{align*}
outside some neighborhood of $\zeta = 0$ in $\Omega$. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point.
\end{itemize}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
\subsubsection{The perturbed operator}
\subsection{Main results}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\begin{thm}
For the regular singular Volterra equation
\[ f = \hardpart f \]
given by an operator of the kind described in Section~\ref{setting:basic}, we have the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.

The size $|f_0|$ goes like $|\zeta|^{\tau-1}$ as $\zeta$ goes to $0$. More precisely, as $|\zeta|$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.

If $\hardpart$ satisfies Condition~\eqref{cond:slow} from Section~\ref{setting:basic}, then $f_0$ is uniformly of exponential type $\lambda$ \textcolor{orange}{[explain what we mean by ``uniformly'']}. In light of the behavior at $\zeta = 0$ described above, this tells us that for every $\Lambda > \lambda$, the solution $f_0$ belongs to the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
\begin{thm}
\textcolor{DarkTurquoise}{Existence and uniqueness for deformed operator}
\end{thm}
\textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect. It's an improved version of the result stated in Section~\ref{frac_int_exist}, which is copied from {\tt airy-resurgence}. Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}
\color{RoyalBlue}
\begin{thm}
Let $\Omega$ be an acute-angled open sector around $\zeta = 0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.} Over $\Omega$, consider a Volterra operator
\[ \mathcal{P} = p + \partial^{-1} \circ q + \mathcal{R}, \]
where
\begin{itemize}
\item $p$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item a simple zero at $\zeta = 0$,
\item no zeros in $\Omega$ (as the next condition implies), and
\item a positive lower bound $C_p |z|^d \le |p|$;
\end{itemize}
\item $q$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item an upper bound $|q| \le C_q |z|^{d-1}$; and
\end{itemize}
\item $\mathcal{R}$ is an integral kernel operator
\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta, \]
where $k$ is a holomorphic function on $\Omega^2$, with
\begin{itemize}
\item an exponential upper bound $k(a, a') \le C_k e^{A|\zeta(a) - \zeta(a')|}$,
\item \textcolor{orange}{[bound K soft]} \[ | k (a, a') |\le \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} e^{\Lambda|\zeta(a)-\zeta(a')|}\]
\end{itemize}
\end{itemize}
Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$, and let $\tau = q_0 / p_1$.

For any $\epsilon > 0$, when the constant $\Lambda > A$ is large enough, the regular singular Volterra equation
\[ \mathcal{P}f = 0 \]
has a unique solution in the affine subspace
\[ \zeta^{\tau-1} + \holoL{\infty, \tau-1+\epsilon}_\Lambda(\Omega) \]
of the function space $\holoL{\infty, \tau-1}_\Lambda(\Omega)$, defined in Section~\ref{fn-spaces}.
\end{thm}
\color{black}
%%\begin{thm}
%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}

@@

%%Under these conditions, let's try to solve the regular singular Volterra equation
%%\[ \mathcal{V}f = 0. \]
%%The leading-order part of the equation,
%%\[ \big[p_1 \zeta + \partial^{-1} \circ q_0\big]f = 0, \]
%%has $\zeta^{\tau-1}$ as a solution, where $\tau = p_1/q_0$. If we guess that the function spaces defined in Section~\ref{fn-spaces} are well suited for this problem, we might hope for the full equation to have a solution of the form
%%\[ f = \zeta^{\tau-1} + f_*, \]
%%where $f_* \in \holoL{\infty, 1-\tau-\epsilon}_Z(\Omega)$ for some $Z \in \C$. When $Z\Omega$ is in the right half-plane and $|Z|$ is large enough, there is in fact a unique solution of this form.
%%\end{thm}
\section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
\subsection{Weighted holomorphic $L^\infty$ spaces}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\cont(\Omega)$ be the space of continuous complex-valued functions on $\Omega$. Give $\cont(\Omega)$ the compact-open topology, recalling that this is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \Omega$~\cite[Example~2.6 and \S 4 notes]{fnl-cpx-anal}. The holomorphic functions form a closed subspace $\holo(\Omega) \subset \cont(\Omega)$~\cite[Proposition~3.14]{fnl-cpx-anal}\textcolor{orange}{[Luecking \& Rubel]}.

Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\Omega$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$. One might describe these functions as being uniformly of exponential type $\Lambda$. They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$. With respect to the seminorm on $\holo(\Omega)$ given by a compact set $K \subset \Omega$, the inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
\begin{prop}\label{exp-complete}
The space $\singexp{0}{\Lambda}(\Omega)$ is complete.
\end{prop}
\begin{proof}
Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$. The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $|f| \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$, so our sequence is Cauchy in $\holo(\Omega)$ too. Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ tells us that for any $r > 0$, we can find some $n$ for which $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$. Since convergence in $\holo(\Omega)$ implies pointwise convergence, we can see as $k$ grows that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$. This shows that our sequence converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$. We can also see from this argument that $f$ is in $\singexp{0}{\Lambda}$: picking some $r > 0$, we observe that
\begin{align*}
e^{-\Lambda |\zeta|}\,|f| & \le e^{-\Lambda |\zeta|}\,|f - f_n| + e^{-\Lambda |\zeta|}\,|f_n| \\
& \le r + \|f_n\|_{0,\Lambda}
\end{align*}
for the corresponding $n$, showing that $e^{-\Lambda |\zeta|}\,|f|$ is bounded.

%%We can also use the Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ to bound the norms $\|f_n\|_{0,\Lambda}$ uniformly over all $n$. Then, from the pointwise convergence argument above, we can draw the additional conclusion that $f$ is in $\singexp{0}{\Lambda}(\Omega)$.
\end{proof}

Now, let's relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$. Let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$. Give it the norm $\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|$. Reprising the arguments from above, we can show that the inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is continuous, and we can generalize Proposition~\ref{exp-complete}:
\begin{prop}
The space $\singexp{\sigma}{\Lambda}(\Omega)$ is complete.
\end{prop}

\subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}
\begin{prop}
    If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{prop}

\begin{proof}
    \begin{align*}
        \|f\|_{\sigma,\Lambda}&=\sup_{\Omega} |\zeta|^{-\sigma}\,  e^{-\Lambda |\zeta|}\, |f|\\
        &= \sup_{\Omega} e^{-\Lambda'|\zeta|}\,|\zeta|^{-\sigma}\,e^{-(\Lambda-\Lambda') |\zeta|}\,|f|\\
        &\leq \sup_\Omega e^{-\Lambda'|\zeta|}\,|\zeta|^{-\sigma}\,|f|\\
        &=\|f\|_{\sigma,\Lambda'}
    \end{align*}
\end{proof}
\color{OrangeRed}
\begin{proof}
    \begin{align*}
        \|f\|_{\sigma,\Lambda}&=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|\\
        &\leq \sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\,|\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
        &=\sup_{\Omega} e^{-(\Lambda-\Lambda') |\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
        &\leq \|f\|_{\sigma,\Lambda'}
    \end{align*}
\end{proof}
\color{black}

\begin{prop}
    If $\Lambda'<\Lambda$ and $\sigma'>\sigma$, the inclusion map $\singexp{\sigma'}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{prop}

\begin{proof}
    \begin{align*}
        \|f\|_{\sigma,\Lambda}&=\sup_{\Omega} |\zeta|^{-\sigma}  e^{-\Lambda |\zeta|} |f|\\
        &= \sup_{\Omega} |\zeta|^{\sigma'-\sigma}\,|\zeta|^{-\sigma'}\,e^{-\Lambda'|\zeta|}\,  e^{-(\Lambda-\Lambda') |\zeta|} \, |f|\\
    \end{align*}
    The function $|\zeta|^{\sigma'-\sigma}\,  e^{-(\Lambda-\Lambda') |\zeta|}$ is bounded near $\zeta = 0$ because the power of $|\zeta|$ is positive, and it's bounded far from $\zeta = 0$ thanks to the decaying exponential. Hence,
    \begin{align*}
       \|f\|_{\sigma,\Lambda}&\leq C\sup_\Omega  |\zeta|^{-\sigma'}\, e^{-\Lambda'|\zeta|} \, |f|\\
        &=C \|f\|_{\sigma',\Lambda'}
    \end{align*}
    for $C = \sup_{\Omega}  |\zeta|^{\sigma'-\sigma}\,  e^{-(\Lambda-\Lambda') |\zeta|}$.
\end{proof}
